Comparing OTU quality across clustering strategies

### 2021-07-17 exploratory/2021/algorithm_diagram.Rmd
DIY plot label so it's inline with mcc

```{r plot_optifit_iters, fig.dim=c(6.875,9.0625), dpi=300}
# TODO custom modifications for loop span & direction
lapply(optifit_iters, function(x) {
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph(title = glue('mcc = {x$edges %>% filter(is_loop) %>% pull(mcc)}'))
}) %>% 
  wrap_plots(ncol = 1) +
  plot_annotation(tag_levels = 'A')
```

>>>>

```{r plot_optifit_iters, fig.dim=c(6.875,9.0625), dpi=300}
# TODO custom modifications for loop span & direction
i <- 0
lapply(optifit_iters, function(x) {
  i <<- i + 1
  tbl_graph(nodes = x$nodes, edges = x$edges) %>% 
    plot_graph(title = glue('{i}) mcc = {x$edges %>% filter(is_loop) %>% pull(mcc)}'))
}) %>% 
  wrap_plots(ncol = 1)
```
